---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# symbolicR

The goal of symbolicR is to provide a R interface to the python module sympy.

Note that currently this package is rather under experiment, if you are interested,
please feel free to give any suggestion, contribute or take over this project.

We have a R package "rSymPy" on CRAN, but the package uses Jython which requires
the Java installation. This package is based on the new reticulate package which
provides a remarkable R interface to python.


## Installation

```{r}
if (!require(reticulate))
    devtools::install_github("rstudio/reticulate")
if (!require(symbolicR))
    devtools::install_github("marlin-na/symbolicR")
```

The package also needs python with numpy and sympy available, you may want to 
use functions from the reticulate package to check.

```{r, eval=FALSE}
reticulate::py_available()
reticulate::py_numpy_available()
reticulate::py_module_available("sympy")
```


## Example


